{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-02-17 documents/acknowledgement.tex
Text and prop improvements
Oh hey the brilluoin just had a bug
Tersenating

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgements}\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Sci-Hub

@@

Profs H. Kassiri, C. David and W. Taylor (among others) at YorkU for encouragement, and H.P. and ice9 for tolerating midnight ramblings.

Thanks to L.H. for wisdom regarding this project, and to my friend Eric, and friends at SimCoLab.

Special thanks to all the people - all equally capable of writing this paper if provided the opportunity - who circumstance led to work menial shifts at the component suppliers that remained open that were so critical. Hopfstader be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance and luck.

@@

{\Large {\verbatim <3}}

>>>>

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Sci-Hub - a very important thought

@@

Profs H. Kassiri, C. David and W. Taylor (among others) at YorkU for encouragement, and friends on twitter for tolerating midnight ramblings.

Thanks to L.H. for wisdom regarding this project, and to my friend Eric, and friends at SimCoLab.
%
%Special thanks to all the people - all equally capable of writing this paper if provided the opportunity - who circumstance led to work menial shifts at the component suppliers that remained open that were so critical. Hopfstader be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance and luck.

@@

{\Large 
	{
\begin{verbatim}
		<3 <3 <3
\end{verbatim}
}}

### 2021-02-17 documents/background.tex
Tersenating

\footnote{"nsPEFs"}

We were inspired to undertake this project by a set of publications by Yang et al, Hung et al, Sun et al.

These reports attempt to establish that, ostensibly unlike human cellular structures, the studied species of viruses coincidentally about the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.

They theoretically model and then experimentally demonstrate in various strains of Influenza A that - supposedly due to this acoustic-resonance effect - the power density levels required to crack the lipid envelope are near the safety limits for continuous exposure to humans.

The experiments are competently designed and many orthogonal measurements are made to confirm the effect.

There are a few minor issues with the experimental technique

These very striking results have attracted some recent attention. \cite{Burkhartsmeier} have observed a resonance of the same nature (see below), and work is proceeding by their team.

Such a non-thermal mechanism is quite unprecedented and extremely dubious, oft-posited but never substantiated; so it has taken some convincing that this is not a particularly abstruse artifact, especially when considered in the context of the broader non-thermal effects literature.

For even the RF power limits set by standards organizations like \cite{ICNIRP2020} \cite{IEEE2006} appear to be based on the observation that any resonance modes which might exist in biological tissues are far too overdamped due to viscous from the surrounding solvent to be of any importance \cite{Vibrational2002}; this is grounded in very solid {\it in vitro}, {\it in vivo} and theoretical evidence.

On the other hand, under clinical and laboratory circumstances, a few well-established non-resonant non-thermal effects have already been put to practical use. An example, electroporation is now a common laboratory procedure, in which an enormous electric field causes ions in solution to migrate across a host cell's membrane. A variant, irreversible electroporation, has been used in the clinic for tumor ablation. In vitro there is evidence to suggest that sub-cellular effects take place under truly tremendous fields.

\lettrine{U}nfortunately, we later realized that for both the absorption cross section and the inactivation mechanism to align as suggested requires the virus, a structure with not more than $6 \times 10^8$ atoms, to have an effective charge of $q=10^7$. It is very difficult to account for such a charge.

@@

While induced polarization is not expected to occur on GHz time scales, especially where solvent ions are the charge carriers, (see ICNIRP arguments), it is possible that some subtle, extremely fast polarization effect regarding electrons could be used to explain this \cite{nature1986}. We have not investigated this in any depth.

On the other hand, Uzunoglu have produced a formulation of the theoretical analysis which requires a very plausible charge of only $q=10^4$.

In another attempt to explain non-thermally, it is possible that this result could be explained by a sort of lipid membrane leakage, attributed to oxidation, which has been observed in strikingly similar regime in liposomes; but this would not necessarily explain the frequency-dependent inactivation seen in Figure 4b of \cite{Efficient2015}.

@@

In any case, this is a very interesting result, and should be replicated with better controls. Gordon Reuben's team appear to be on the case, so we will not address this regime, 100 V/m, 15 minute, 8 GHz, any further.

Were such a mechanism to exist, it would seem to provide significant advantages over existing UV or cold-plasma sterilization;

We leave this section here because it will be useful to inform us in the next section.

There are some 20,000 papers on the topic of RF safety, with solid mechanistic, in vitro, in vivo and epidemiological evidence of safety in the 2.4 GHz and 5.8 GHz bands.

However, "There are limited experimental human data upon which to set limits on exposures above 6 GHz" [Chan 2019]. Only 2\% of the above papers are on frequencies $>6$ GHz [Vijayalaxmi 2018].

In addition, what data remains in this category is of varying quality.

As has been starkly demonstrated in the recent hydroxychloroquine contradictions [Gautret 2020] [Geleris 2020], biological research must be essentially perfectly conducted to offer any meaningful results.

So, turning to, we find an entirely new set of problems. This effect is presumed to depend on mechanical forces of the entire virus. The large scales of physical virology all but prevent all-atom simulations that include the genome, but the genome is essential to the effectiveness of this technique. The same reasons currently rule out simulations including chemical reactions, important for lipid oxidation effects. Attempts at coarse-graining require careful tuning \footnote{or "parameterizing" in MD parlance}, where slight mis-steps in problem setup can lead to unphysical effects that completely alter the conclusion, particularly where solvent polarization. The kind which can only be obtained through extensive hard-wrought expertise (which the author does not possess) and careful verification,

Multiscale or hybrid techniques would seem to offer one route out of this pickle. Simulating a small patch of lipid in explicit solvent, with the pressure provided by

The stymied writer turns to writing inconclusive high-level summaries which lack sufficient detail to be of true use.

First, free-space techniques are easily implemented to prevent respiratory transmission. A \$10 emitter appears to suffice on a personal level, and \$100 systems for room-scale.\\

Second, via cursory FDTD simulations, using off-the-shelf equipment and modified non-invasive microwave diathermy techniques, it appears to be possible to inactivate all virions in the outer 2 cm of the lungs and inner 1 cm of the bronchi without any effect on the surrounding tissue.

One might be tempted to cite long wavelength of microwaves as an advantage. A UV photon is approximately the same wavelength as the virus itself;  In the case of, the wavelength is >> diameter, meaning that

Like pumping a swing, this effect allows an otherwise inconsequential field magnitude to store energy over a small number of cycles until the virus is destroyed. \\
\\\\

It is common for.  However, in the classical case, a non-zero resonant frequency requires the ratio of the loss in energy to the surroundings to the oscillating mass to obey $b/(2m) < \omega_{res} \sqrt{2}$ \cite{Driven}; the solution to the harmonic oscillator equation is piecewise around this value.

(unless the various small-scale quantum mechanical oscillators are considered, which in our case appear to require fields in excess of 1 TW to access).

Most things with a stiffness matrix has some resonant frequency\citationneeded. As far as we can tell, two justifications underpin the categorical implausibility of resonance-like behavior in

@@

\begin{itemize}
	\item Viscous damping from biological solvents is so strong that the relaxation time is 
\end{itemize}

To a first order, this simply doesn't seem to be true in the case of the virion.

\begin{itemize}
	\item The charge 
\end{itemize}

\footnote{It should be noted that this {\it confined} acoustic resonance is subtly distinct from common-and-garden pipe-organ acoustic resonance; this is apparently not a strictly classical phenomenon. Besides standard Coulomb-like and Lennard-Jones-like interactions between constituent particles, if Fr\"{o}hlich is to be believed at these nanoscopic scales there are also wave-function interactions among the particles of the virus which can shift storage to modes not otherwise expected.

	We confess to not yet understanding this phenomenon; fortunately, while helpful, the details of how this mode appears are not critical to implementing this technique.}

@@

the only analagous non-thermal mechansism we are aware of is electroporation; and that requires the diffusion of ionized sodium and potassium charge carriers through the membrane, which would seem to necessarily require a non-

So far as we are aware, there are no fundamental physical obstacles to non-thermal effects in biological systems.

This may account for why this paper has been largely ignored.

The precise structure and charge of the virion appears to be a singular anomaly in this otherwise categorical non-existence.

Any technique that requires background subtraction (see).

We distinct regimes, which overlap in physical mechanisms (both involve the charge distribution and relaxation time) but which cite different bodies of literature. Vestiges

frequency-dependent inactivation

(gordon reuben following up)

After the relaxation time, the energy is a distant memory; only the mechanical effects that were induced during that time can remain. Since the energy is too small to

@@

I was hoping I would have a definitive demonstration, so as to not redirect resources from more promising avenues.

Note that it is possible that this has already been worked on. The last review was several months ago, and the literature is changing very rapidly. Reuben

Much of the work in this paper was concerned with this paper

@@

On the other hand, 0.5 angstroms is only a 0.04\% deflection of the capsid, whereas a general value for host cells is about 3\% deflection.

Certainly the virus will be destroyed at some finite electric field. It remains to be seen whether a practical limit

 \cite{Resonance1996}

@@

suggestive, especially because a model organism

@@

On the other hand, the maximum amplitude of oscillation is only expected to be on the order of 50 picometers.

@@

for which our working hypothesis is that there are no clinically useful mechanisms,

It stands to reason, then, that any pulse longer than the relaxation time is not efficiently.

vestiges

@@

as dt decreases, there's lots of room to add more zeros. a pulse 4 orders of magnitude higher than the maximum field used by practically any existing system.

@@

The effects that we are concerned with occur 4 orders of magnitude above

Windows between caused by structural or

Additionally, other sterilization techniques may produce superior results with less faffing about and should be evaluated in the same context. For instance, data on far UV\cite{Germicidal2017} indicates safety.\\

"Windows" of the same sort have been found, both in thermal and pulsed ultra-high-power UV Prodouz \cite{Use1987a}.

(more data exists for influenza A; it is sufficiently structurally similar that ).

Excellent theoretical arguments against the possibility of non-thermal effects can be found Adair \cite{Vibrational2002}, Adair \cite{Biological2002}, and Foster \cite{Viscous2000} on microtubules.

Adair \cite{Biophysics2000} on Brillouin.

\nameref{sec:viscousdamping}

Data cannot be trusted implicitly. By time-domain spectrometry (a reasonably trustworthy technique), Miura \cite{Microwave1994} find

Owrutsky Vibrational1994

We don't want a purely membrane-electroporative effect since the lipid membrane of the virus is similar to (derived from) the host cell and little selectivity can be expected. Unless the virus has a lower capacitance and charges faster than the cell.

Also, the pore must stay open for long enough that damage is dealt to the virus.

Scope for this effect can be seen in the following contrast. The statement which echos the concensus of a number of literature reviews by standards organizations:

@@

Schnelle\cite{Trapping1996}

@@

and Fuhr\cite{Radiofrequency1994} and Grom \cite{Accumulation2006} report on a modification of so-called dielectrophoresis techniques called electrorotation, in a so-called field cage.

Rotation is sub-synchronous at a few dozen Hz, whereas the field rotates at between 0.1 MHz to over 50 MHz; in most cases the frequency is made high enough that ion does not occur.

In the virus tests by Schnelle, a field of 0.3 MV/m was used, without apparent damage to the virus, though their

Gimsa \cite{New1999} use a four-electrode cage at 25 kV/m

@@

\subsection{Liburdy's oxygen-dependent lipid leakage}

@@

Vijayalaxmi \cite{Biological2016} \cite{Comprehensive2018} \cite{Funding2019} already offer a number of excellent guidelines on best practices in this field; as do Chou \cite{chou1996radio}. We only offer a few issues which we were particularly concerned about when designing our experiments and searching literature.

>>>>

We were inspired to undertake this project by a set of publications by a certain Sun group, (primarily Liu et al \cite{Microwave2009} and Yang et al \cite{Efficient2015}, simultaneously demonstrated by Hung et al \cite{focusing2014}).

These reports attempt to establish that, ostensibly unlike human cellular structures, the studied species of viruses have about the right size, shape, stiffness, and net charge distribution such that the lowest normal mode is slightly underdamped and can be driven by intense electric fields.

The group theoretically model and then experimentally demonstrate in various strains of Influenza A that - supposedly due to this acoustic, normal-mode effect - the field intensity required to crack the lipid envelope is near the safety limits for continuous exposure to humans.

The experiments are competently designed and many orthogonal measurements are made to suggest that such an effect exists.

There are a few minor issues with the experimental technique (see discussion below).

These results have attracted some recent attention. \cite{Optical2020} have observed a normal mode of the same nature optically, and work is proceeding by their team.

However, such a non-thermal mechanism is quite unprecedented and extremely dubious, oft-posited but never substantiated; so it has taken some convincing that this is not a particularly abstruse artifact, especially when considered in the context of the broader non-thermal effects literature.

For even the RF power limits set by standards organizations like \cite{ICNIRP2020} \cite{IEEE2006} appear to be based on the observation that any resonance modes which might exist in biological tissues are categorically overdamped due to viscous from the surrounding solvent to be of any importance \cite{Vibrational2002}, and such charge distributions do not lend themselves to sufficiently strong coupling to external fields. This is grounded in very solid {\it in vitro}, {\it in vivo} evidence and theoretical modelling.

On the other hand, under clinical and laboratory circumstances, a few well-established non-resonant non-thermal effects have already been put to practical use.

As an example, electroporation is now a common laboratory procedure in which an enormous electric field causes ions in solution to diffuse across a host cell's membrane, reversibly rendering it permeable (among other, more subtle mechanisms; the minutia of poration are extraordinarily complex and beyond the author's understanding\cite{Theoretical2007}).

A variant using irreversible electroporation\cite{Irreversible2013} has recently been used in the clinic\cite{Nonthermal2013} for tumor ablation.% In vitro there is evidence to suggest that sub-cellular effects take place under truly tremendous fields.

\lettrine{U}nfortunately, it appears that, in order to fit Yang et al's observed data on absorption cross section, and to explain the suggested inactivation mechanism, requires that the virus, a structure with not more than $6 \times 10^8$ atoms and not more than $1 \times 10^8$ solvent molecules, to have an effective charge of $q=10^7$. It is difficult to account for such a charge.

On the other hand, Uzunoglu have produced a formulation of the theoretical analysis which requires a more plausible charge of only $q=10^4$. However, whether even this charge is reasonable given solvent screening is not yet known to us.\footnotemark

@@

\footnotetext{While induced polarization is not expected to occur on GHz time scales, especially where solvent ions are the charge carriers, (see ICNIRP arguments), it is possible that some subtle, extremely fast polarization effect regarding electrons could be used to explain this \cite{nature1986}. We have not investigated this in any depth.}

It is possible that this result could be due to a specific sort of lipid membrane leakage, attributed to oxidation, which has been observed in strikingly similar regime in liposomes (\hyperref[sec:liburdy]{c.f.}); but this would not easily explain the frequency-dependent inactivation seen in Figure 4b of \cite{Efficient2015}.

@@

In any case, this is a very interesting result, and should be replicated with better controls. Reuben's team appear to be on the case, so we will not address this regime, a 15 minute, 100 V/m, 8 GHz, exposure, in much detail.\\

Were such a mechanism to exist, it would seem to provide significant advantages over existing Far UV or cold-plasma sterilization.

%We leave this section here because it will be useful to inform us in the next section.

%
%
%There are some 20,000 papers on the topic of RF safety, with solid mechanistic, in vitro, in vivo and epidemiological evidence of safety in the 2.4 GHz and 5.8 GHz bands.
%
%However, "There are limited experimental human data upon which to set limits on exposures above 6 GHz" [Chan 2019]. Only 2\% of the above papers are on frequencies $>6$ GHz [Vijayalaxmi 2018]. 
%
%In addition, what data remains in this category is of varying quality. 
%
%
%
%As has been starkly demonstrated in the recent hydroxychloroquine contradictions [Gautret 2020] [Geleris 2020], biological research must be essentially perfectly conducted to offer any meaningful results.
%
%So, turning to, we find an entirely new set of problems. This effect is presumed to depend on mechanical forces of the entire virus. The large scales of physical virology all but prevent all-atom simulations that include the genome, but the genome is essential to the effectiveness of this technique. The same reasons currently rule out simulations including chemical reactions, important for lipid oxidation effects. Attempts at coarse-graining require careful tuning \footnote{or "parameterizing" in MD parlance}, where slight mis-steps in problem setup can lead to unphysical effects that completely alter the conclusion, particularly where solvent polarization. The kind which can only be obtained through extensive hard-wrought expertise (which the author does not possess) and careful verification, 
%
%Multiscale or hybrid techniques would seem to offer one route out of this pickle. Simulating a small patch of lipid in explicit solvent, with the pressure provided by
%
%The stymied writer turns to writing inconclusive high-level summaries which lack sufficient detail to be of true use.
%
%
%
%
%
%First, free-space techniques are easily implemented to prevent respiratory transmission. A \$10 emitter appears to suffice on a personal level, and \$100 systems for room-scale.\\
%
%
%Second, via cursory FDTD simulations, using off-the-shelf equipment and modified non-invasive microwave diathermy techniques, it appears to be possible to inactivate all virions in the outer 2 cm of the lungs and inner 1 cm of the bronchi without any effect on the surrounding tissue. 
%
%
%
%
%One might be tempted to cite long wavelength of microwaves as an advantage. A UV photon is approximately the same wavelength as the virus itself;  In the case of, the wavelength is >> diameter, meaning that 
%
%
%
%
%Like pumping a swing, this effect allows an otherwise inconsequential field magnitude to store energy over a small number of cycles until the virus is destroyed. \\
%\\\\
%
%
%It is common for.  However, in the classical case, a non-zero resonant frequency requires the ratio of the loss in energy to the surroundings to the oscillating mass to obey $b/(2m) < \omega_{res} \sqrt{2}$ \cite{Driven}; the solution to the harmonic oscillator equation is piecewise around this value. 
%
%(unless the various small-scale quantum mechanical oscillators are considered, which in our case appear to require fields in excess of 1 TW to access).
%
%
%Most things with a stiffness matrix has some resonant frequency\citationneeded. As far as we can tell, two justifications underpin the categorical implausibility of resonance-like behavior in 
%

@@

%
%\begin{itemize}
%	\item Viscous damping from biological solvents is so strong that the relaxation time is 
%\end{itemize}
%
%To a first order, this simply doesn't seem to be true in the case of the virion.
%
%
%
%
%
%\begin{itemize}
%	\item The charge 
%\end{itemize}
%
%\footnote{It should be noted that this {\it confined} acoustic resonance is subtly distinct from common-and-garden pipe-organ acoustic resonance; this is apparently not a strictly classical phenomenon. Besides standard Coulomb-like and Lennard-Jones-like interactions between constituent particles, if Fr\"{o}hlich is to be believed at these nanoscopic scales there are also wave-function interactions among the particles of the virus which can shift storage to modes not otherwise expected.
%	
%	We confess to not yet understanding this phenomenon; fortunately, while helpful, the details of how this mode appears are not critical to implementing this technique.}

@@

%
%So far as we are aware, there are no fundamental physical obstacles to non-thermal effects in biological systems. 
%
%
%This may account for why this paper has been largely ignored.
%
%The precise structure and charge of the virion appears to be a singular anomaly in this otherwise categorical non-existence.
%
%
%
%
%
%Any technique that requires background subtraction (see).
%
%
%We distinct regimes, which overlap in physical mechanisms (both involve the charge distribution and relaxation time) but which cite different bodies of literature. Vestiges

@@

@@

On the other hand, a 0.5 angstrom movement is only a 0.04\% deflection of the capsid, whereas a general value for host cells is about 3\% deflection. In addition, with a relaxation time on the order of 500 ps, it is difficult to imagine that the energy will be sufficiently concentrated to be destructive, as after the relaxation time the energy is a distant memory; only the mechanical effects that were induced during that time can remain.

At least we do not have to justify observing an effect at an exposure of $10^{-17} W/m^2$ \cite{Resonance1996}.

Certainly the virus will be destroyed at some finite electric field.

@@

%
%suggestive, especially because a model organism
\clearpage

@@

%
%On the other hand, the maximum amplitude of oscillation is only expected to be on the order of 50 picometers. 
%

@@

%for which our working hypothesis is that there are no clinically useful mechanisms,

It stands to reason, then, that any pulse longer than the relaxation time is not efficiently using the non-thermal nature of the effect.

@@

%as dt decreases, there's lots of room to add more zeros. a pulse 4 orders of magnitude higher than the maximum field used by practically any existing system.

@@

%The effects that we are concerned with occur 4 orders of magnitude above

%Windows between caused by structural or

%Additionally, other sterilization techniques may produce superior results with less faffing about and should be evaluated in the same context. For instance, data on far UV\cite{Germicidal2017} indicates safety.\\
%
%"Windows" of the same sort have been found, both in thermal and pulsed ultra-high-power UV Prodouz \cite{Use1987a}.
%
%(more data exists for influenza A; it is sufficiently structurally similar that ).
%
%Excellent theoretical arguments against the possibility of non-thermal effects can be found Adair \cite{Vibrational2002}, Adair \cite{Biological2002}, and Foster \cite{Viscous2000} on microtubules. 
%
%
%
%Adair \cite{Biophysics2000} on Brillouin.
%
%\nameref{sec:viscousdamping}
%
%Owrutsky
%
%We don't want a purely membrane-electroporative effect since the lipid membrane of the virus is similar to (derived from) the host cell and little selectivity can be expected. Unless the virus has a lower capacitance and charges faster than the cell.
%
%Also, the pore must stay open for long enough that damage is dealt to the virus. 
%

%Scope for clinical utility for this effect can be seen in the following contrast.

Recent data by de Seze following continuous exposure to nanosecond fields at an external field of 3 MV/m \cite{Repeated2020} notes no acute effects, but

The following statement echos the concensus of a number of literature reviews by standards organizations:

@@

@@

Schnelle\cite{Trapping1996} and Fuhr\cite{Radiofrequency1994} and Grom \cite{Accumulation2006} and Gimsa \cite{New1999} report on using a modification of so-called dielectrophoresis techniques called electrorotation, in a so-called field cage.

Such electrorotation is always sub-synchronous (unlike optical centrifuge techniques) at a few dozen Hz, whereas the field rotates at between 0.1 MHz to over 50 MHz; in most cases the frequency is made high enough that ion does not occur.

In the virus tests by Schnelle, a field of 0.3 MV/m was used, without apparent damage to the virus.

Gimsa \cite{New1999} use a four-electrode cage at 25 kV/m to trap influenza.

@@

\subsection{Liburdy's oxygen-dependent lipid leakage}
\label{sec:liburdy}

@@

Vijayalaxmi \cite{Biological2016} \cite{Comprehensive2018} \cite{Funding2019} already offer a number of excellent guidelines on best practices in this field; as do Chou \cite{chou1996radio} and \cite{Effects2016} . We only offer a few issues which we were particularly concerned about when designing our experiments and searching literature.

### 2021-02-17 documents/brillouin_pulse_math.tex
Tersenating

\begin{figure}[H]
	%	\makebox[\textwidth][c]{
	\includesvg[width=\textwidth]{propagated_waveforms_detail}
	\caption{\\
		Some input (left) and output (right) waves (without considering oscillator coupling) transmitted through 6 cm of muscle.\\
		X axis is time; Y axis is amplitude.
		(a) Gaussian monopulse with 16 ps FWHM.\\
		(b) Optimized 10 GHz sawtooth wave. Note the slight high-frequency ripple.\\ This has a frequency of approximately 1.5 GHz.\\
		(c) Prototypical precursor 10 GHz sine burst.\\
		(d) Continuous 10 GHz sine tone.
}
\end{figure}

@@

>>>>

\begin{figure}[H]
	%	\makebox[\textwidth][c]{
	\includesvg[width=\textwidth]{propagated_waveforms_detail}
	\caption{\\
		Some input (left) and output (right) waves (without considering oscillator coupling) transmitted through 6 cm of muscle.\\
		X axis is time; Y axis is amplitude.\\
		(a) Gaussian monopulse with 16 ps FWHM.\\
		(b) Optimized 10 GHz sawtooth wave. Note the slight high-frequency ripple.\\ This has a frequency of approximately 1.5 GHz.\\
		(c) Prototypical precursor 10 GHz sine burst.\\
		(d) Continuous 10 GHz sine tone.
}
\end{figure}

@@

Producing such arbitrary electrical impulses may seem implausible; but in fact, if is a sufficiently sharp and only a few cycles are required,

can probably be produced by e.g. an Auston switch feeding a pulse shaping line.
